Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-07-12 main.tex
Updates from Overleaf

    \item \textbf{Initial Sample Selection}. In this step, we take the output catalog from the previous step and remove those objects that are not likely to be LSBGs of interest. To be specific, we require objects have $g$-band half-light radius (measured by Source Extractor) larger than $r_{\rm min} = 2.0\arcsec$. We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$. %These cuts are the same as in \citetalias{Greco2018}. 
    \textbf{Morphology? Auto-correlation?}

@@

\subsection{Completeness}

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{completeness.pdf}
	}
	\caption{Caption}
	\label{fig:completeness}
\end{figure*}

@@

\textbf{Make sure that completeness is assigned based on the bias-corrected size and SB.}

\subsection{Modeling and measurement error}\label{sec:modeling}
Although vanilla scarlet does a good job on removing false positives, the measured size, magnitude, and surface brightness on the vanilla scarlet model are quite biased. These measurements cannot be used to derive the physical properties of LSBGs.

@@

After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left. Then we match them to the LSBG catalog (described in Section \ref{sec:detection}) as follows. For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}. It turns out that 40\% of hosts have virial radii larger than 300 kpc. Then we identify any LSBG that falls into the projected angular virial radius of the host. Then these LSBGs are associated with the host. We repeat this process for all hosts. If one LSBG is associated to multiple hosts, we assign it to the nearest host (normalized by the angular size of virial radius). In the end, we have 901 MW-like hosts and 8,367 LSBG candidates associated with them. However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shrreded large galaxies, compact sources in galaxy outskirts, etc. In the following, we perform a deblending step to effectively remove these spurious objects.

@@

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{size_distribution.pdf}
    \caption{Caption}
    \label{fig:size_distribution}
\end{figure}

@@

Homework:
1. 1-sigma definition, UPG
2. number of UDG per host, as a function of host mass bins.
3. Move the stellar mass bin definition, try to match with red/blue, spiral/elliptical plot. If cannot match, does this hint the formation scenarios?
4. How significant do we detect blue UDGs? 
5. Split into redshift bins

TODO:
1. rerun the matching, compensate the left ~1000 LSBGs.
2. galactic extinction.

@@

\section*{Acknowledgment}
JL is grateful for discussions with XXX.

\software{\href{http://www.numpy.org}{\code{NumPy}} \citep{Numpy},
          \href{https://www.astropy.org/}{\code{Astropy}} \citep{astropy}, \href{https://www.scipy.org}{\code{SciPy}} \citep{scipy}, \href{https://matplotlib.org}{\code{Matplotlib}} \citep{matplotlib},
          \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017},
          \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}, \href{https://github.com/dr-guangtou/unagi}{\code{unagi}}.
          }

@@

\begin{table}
\caption{UDG (UPG) catalog description} 
\label{tab:catalog}
\begin{center}
\begin{tabular}{l l l}
\hline\hline
% \multicolumn{3}{c}{Table: LSBGs (781 rows)}                 \\
% \hline
Column Name      & Unit    & Description                    \\
\hline
ID                       &         & Unique LSBG ID \\
ra                       & deg     & Right ascension (J2000) \\
dec                      & deg     & Declination (J2000) \\
$r_e$         & arcsec  & Circularized effective radius  \\
$\sigma(r_e)$ & arcsec  & Uncertainty of $r_e$ \\
$\overline{\mu}_{\mathrm{eff}}(g)$               & \sbunit & $g$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(g))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(g)$           \\
$\overline{\mu}_{\mathrm{eff}}(r)$               & \sbunit & $r$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(r))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(r)$           \\
$\overline{\mu}_{\mathrm{eff}}(i)$               & \sbunit & $i$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(i))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(i)$           \\
$m_g$                    & mag     & $g$-band apparent magnitude     \\
$\sigma(m_g)$            & mag     & Uncertainty of $m_g$            \\
$m_r$                    & mag     & $r$-band apparent magnitude     \\
$\sigma(m_r)$            & mag     & Uncertainty of $m_r$            \\
$m_i$                    & mag     & $i$-band apparent magnitude     \\
$\sigma(m_i)$            & mag     & Uncertainty of $m_i$            \\
$g-r$                    & mag     & $g-r$ color                     \\
$\sigma(g-r)$           & mag     & Uncertainty of $g-r$ color      \\
$g-i$                    & mag     & $g-i$ color                     \\
$\sigma(g-i)$           & mag     & Uncertainty of $g-i$ color      \\
$\nu$                    &         & Spergel index              \\
$\varepsilon$               &         & Ellipticity                     \\
$A_g$                    & mag     & $g$-band Galactic extinction \\
$A_r$                    & mag     & $r$-band Galactic extinction \\
$A_i$                    & mag     & $i$-band Galactic extinction \\
\hline\hline
\end{tabular}
\end{center}
\tablecomments{
These tables are published in their entirety in machine-readable format.
Magnitudes are on the AB system and have not been corrected for Galactic
extinction. We provide Galactic extinction corrections, which are derived from
the \citet{Schlafly:2011aa} recalibration of the \citet{Schlegel:1998aa} dust maps. 
}
\end{table}

>>>>

    \item \textbf{Initial Sample Selection}. In this step, we take the output catalog from the previous step and remove those objects that are not likely to be LSBGs of interest. To be specific, we require objects have $g$-band half-light radius (measured by Source Extractor) larger than $r_{\rm min} = 2.0\arcsec$. We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$. %These cuts are the same as in \citetalias{Greco2018}. 
    \textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}

@@

\subsection{Modeling}\label{sec:modeling}
Although vanilla scarlet does a good job on removing false positives, the measured size, magnitude, and surface brightness on the vanilla scarlet model are quite biased. These measurements cannot be used to derive the physical properties of LSBGs.

We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}. Overall speaking, the measurement agrees with the truth quite well. However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$ is under-estiamted. We also characterize the bias and the scatter in measurement as a function of size and surface brightness. We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.

\subsection{Completeness and Measurement Uncertainty}

\subsubsection{Completeness}\label{sec:completeness}
\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{completeness.pdf}
	}
	\caption{Caption}
	\label{fig:completeness}
\end{figure*}

@@

%\textbf{Make sure that completeness is assigned based on the bias-corrected size and SB.} Checked. No problem.

\subsubsection{Measurement uncertainty}\label{sec:meas_unc}
We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}. Overall speaking, the measurement agrees with the truth quite well. However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$\sbunit is under-estiamted. We also characterize the bias and the scatter in measurement as a function of size and surface brightness. We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.

In order to test how well do we recover the photometric and structural parameters in the modeling step (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile. We compare the fitting results with the ground truth in Figure \ref{fig:meas_bias}, where $\Delta(X) = X(\rm truth) - X(\rm measured)$, and x-axis corresponds to the truth values. We find that the measured half-light radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and apparent size. For surface brightness fainter than 27\ \sbunit, the measured size can be much smaller than the truth. As a result, the apparent magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than the truth.

To correct for this bias in size, surface brightness, apparant magnitude, and color, we assume that the bias only depends on the size and surface brightness. Indeed, we do not find any significant dependence of the bias on color, ellpticity, and Spergel index. We split the $r_e-\overline{\mu}_{\rm eff}(g)$ plane using a $8\times 8$ grid, and calculate the mean bias within each bin. Then we interpolate over the grid using a multiquadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}. Figure \ref{fig:meas_err} shows the interpolated bias terms as a function of the measured size and surface brightness. For half-light radius, we take $(r_{e, \rm t} - r_{e, \rm m}) / r_{e,\rm m}$ as the bias term; for surface brightness, we take $\overline{\mu}_{\rm eff, t}(g) - \overline{\mu}_{\rm eff, m}(g)$ as the bias term. As shown in Figure \ref{fig:meas_err}, the size and surface brightness bias grows as increasing surface brightness. The bias has a peak at $r_e\sim 6\arcsec$ because the $r_e$ shown in the figure is the measured size, not the truth size. It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$. We also find that the bias in $g-i$ color is quite small.

For LSBGs in our sample, we apply corrections for the bias using the interpolated bias terms. We first correct for the bias in size, $g$-band average surface brightness, $g-r$ and $g-i$ colors. Then we calculate the $g$-band apparent magnitude following $m_g = \overline{\mu}_{\rm eff}(g) - 2.5\log(2\pi r_e^2)$. The magnitudes and surface brightnesses in other bands are derived using $g$-band magnitude, surface brightness, and colors. In this way, we apply a self-consistent correction for the measurement bias to the data.

Besides, it is also important to characterize the measurement uncertainty. The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, contamination effects, etc. Unlike other parametric modeling code such as \code{galfit} or \code{imfit}, \code{scarlet} does not explore the full likelihood (posterior) space but rather finds one optimial solution. Thus we cannot get a statistical error of the measured properties from \code{scarlet}. However, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor. Following the same way of calculating the bias, in each bin, we compute the standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid. The measurement errors are shown in Figure \ref{fig:meas_err} as contours.

TBD: re-think the way of computing the error, especially for $r_e$.

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{meas_bias.pdf}
	}
    \caption{Caption}
    \label{fig:meas_bias}
\end{figure*}

@@

After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left. Then we match them to the LSBG catalog (described in Section \ref{sec:detection}) as follows. For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}. It turns out that 40\% of hosts have virial radii larger than 300 kpc. Then we identify any LSBG that falls into the projected angular virial radius of the host. Then these LSBGs are associated with the host. We repeat this process for all hosts. If one LSBG is associated to multiple hosts, we assign it to the nearest host (normalized by the angular size of virial radius). Finally, we have 901 MW-like hosts and 8,367 LSBG candidates associated with them. However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shrreded large galaxies, compact sources in galaxy outskirts, etc. In the following, we perform a deblending step to effectively remove these spurious objects.

@@

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{size_distribution.pdf}
	}
    \caption{Caption}
    \label{fig:size_distribution}
\end{figure*}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{radial_distribution.pdf}
	}
    \caption{Caption}
    \label{fig:radial_distribution}
\end{figure*}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{N_UDG_host_mass.pdf}
	}
    \caption{Caption}
    \label{fig:n_udg}
\end{figure*}

@@

Homework:
1. 1.5-sigma definition, UPG
2. number of UDG per host, as a function of host mass bins.
3. Move the stellar mass bin definition, try to match with red/blue, spiral/elliptical plot. If cannot match, does this hint the formation scenarios?
4. How significant do we detect blue UDGs? 
5. Split into redshift bins

TODO:
1. rerun the matching, compensate the left ~1000 LSBGs.
2. galactic extinction. Done!!!

@@

\section*{Acknowledgment}
JL is grateful for discussions with XXX. The authors thank Yao-Yuan Mao for his tool for visualizing image cutouts.

The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of Japan and Taiwan, and Princeton University. The HSC instrumentation and software were developed by National Astronomical Observatory of Japan (NAOJ), Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU), University of Tokyo, High Energy Accelerator Research Organization (KEK), Academia Sinica Institute for Astronomy and Astrophysics in Taiwan (ASIAA) and Princeton University.  
Funding was contributed by the FIRST program from Japanese Cabinet Office, Ministry of Education, Culture, Sports, Science and Technology (MEXT), Japan Society for the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), Toray Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA and Princeton University.
\vspace{1em}
\software{\href{http://www.numpy.org}{\code{NumPy}} \citep{Numpy},
          \href{https://www.astropy.org/}{\code{Astropy}} \citep{astropy}, \href{https://www.scipy.org}{\code{SciPy}} \citep{scipy}, \href{https://matplotlib.org}{\code{Matplotlib}} \citep{matplotlib},
          \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017},
          \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}, \href{https://github.com/dr-guangtou/unagi}{\code{unagi}}.
          }

@@

\begin{table}
\caption{UDG (UPG) catalog description} 
\label{tab:catalog}
\begin{center}
\begin{tabular}{l l l}
\hline\hline
% \multicolumn{3}{c}{Table: LSBGs (781 rows)}                 \\
% \hline
Column Name      & Unit    & Description                    \\
\hline
ID                       &         & Unique LSBG ID \\
ra                       & deg     & Right ascension (J2000) \\
dec                      & deg     & Declination (J2000) \\
$r_e$         & arcsec  & Circularized effective radius  \\
$\sigma(r_e)$ & arcsec  & Uncertainty of $r_e$ \\
$\overline{\mu}_{\mathrm{eff}}(g)$               & \sbunit & $g$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(g))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(g)$           \\
$\overline{\mu}_{\mathrm{eff}}(r)$               & \sbunit & $r$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(r))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(r)$           \\
$\overline{\mu}_{\mathrm{eff}}(i)$               & \sbunit & $i$-band average surface brightness within $r_e$ \\
$\sigma(\overline{\mu}_{\mathrm{eff}}(i))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(i)$           \\
$m_g$                    & mag     & $g$-band apparent magnitude     \\
$\sigma(m_g)$            & mag     & Uncertainty of $m_g$            \\
$m_r$                    & mag     & $r$-band apparent magnitude     \\
$\sigma(m_r)$            & mag     & Uncertainty of $m_r$            \\
$m_i$                    & mag     & $i$-band apparent magnitude     \\
$\sigma(m_i)$            & mag     & Uncertainty of $m_i$            \\
$g-r$                    & mag     & $g-r$ color                     \\
$\sigma(g-r)$           & mag     & Uncertainty of $g-r$ color      \\
$g-i$                    & mag     & $g-i$ color                     \\
$\sigma(g-i)$           & mag     & Uncertainty of $g-i$ color      \\
$\nu$                    &         & Spergel index              \\
$\varepsilon$               &         & Ellipticity                     \\
$A_g$                    & mag     & $g$-band Galactic extinction \\
$A_r$                    & mag     & $r$-band Galactic extinction \\
$A_i$                    & mag     & $i$-band Galactic extinction \\
\hline\hline
\end{tabular}
\end{center}
\tablecomments{
These tables are published in their entirety in machine-readable format.
Magnitudes are on the AB system and have not been corrected for Galactic
extinction. We provide Galactic extinction corrections, which are derived from
the \citet{Schlafly2011} recalibration of the \citet{SFD1998} dust maps. 
}
\end{table}
